---
title: "Template"
subtitle: "Class"
author: "Gabriel Herrera-Lim - `r format(Sys.Date(), '%b %d, %Y')`"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float: true
    toc_depth: 3
    includes:
      after_body: footer.html
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

<style>
#TOC {
  background: url("https://seeklogo.net/wp-content/uploads/2018/10/notre-dame-fighting-irish-logo.png");
  background-size: 64px 64px;
  background-position: top center;
  padding-top: 60px !important;
  background-repeat: no-repeat;
}
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
  color: #D39F10;
  background-color: #0C2340;
  font-family: Avenir Next;
  font-weight: 600;
}
.list-group-item {
  color: #0C2340;
  background-color: #D39F10;
}
.nav>li>a {
  position: relative;
  display: block;
  color: #D39F10;
  background-color: white;
}
  .nav>li>a:hover {
    background-color: #D39F10;
    color: #0C2340;
  }
.nav-pills > li.active > a, .nav-pills > li.active > a:focus {
  color: #D39F10;
  background-color: #0C2340;
}
  .nav-pills > li.active > a:hover {
    background-color: #D39F10;
    color: #0C2340;
  }
</style>

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
      font-family: Avenir Next;
      color: 0C2340;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: #0C2340;
  font-family: Avenir Next;
  font-style: bold;
  font-weight: 800;
  padding-top: 10px;
  text-align: center;
  text-decoration: underline;
  margin-top: 20px;
  margin-bottom: 5px;
}
h3.subtitle {
  font-size: 25px;
  color: #AE9142;
  font-family: Avenir Next;
  font-style: bold;
  font-weight: 800;
  text-align: center;
  margin: 0px;
}
h4.author {
  font-size: 20px;
  color: #AE9142;
  font-family: Avenir Next;
  font-style: bold;
  font-weight: 500;
  text-align: center;
  margin: 0px;
}
h2 { /* Header 3 */
  font-size: 18px;
  font-family: Avenir Next;
  color: #0C2340;
  font-weight: 700;
}
code.r{ /* Code block */
    font-size: 12px;
    font-family: Avenir Next;
    color: #AE9142;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 10px;
    font-family: Avenir Next;
    color: #AE9142;
}
blockquote {
    padding: 10px 20px;
    margin: 0 0 20px;
    font-size: 12px;
    border-left: 5px solid #AE9142;
}
</style>

***

## Part I {.tabset .tabset-fade .tabset-pills}

### **Part I-A**

```{r}

```

